---
title: "Untitled"
author: "Fernan Gaillardou"
date: "2022-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Packages
```{r}
library(tidyverse)
library(readxl)
library(tuber)
library(purrr)
```
1) Make your own request to the YouTube API for a different seed video.
```{r}
yt_oauth("791684141006-35su4lb2stjkhjbkp40lqugp6fd6ud2i.apps.googleusercontent.com","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")
startvid <- "LQtp1USYjcA"
rel_vids <- get_related_videos(startvid, max_results = 50, safe_search = "none")
```
2) Collect one video ID for each of the channels included in the resulting data
```{r}
q2 <- rel_vids %>% 
  group_by(channelId) %>% sample_n(1)
```
3) Write a for loop to collect recommended videos for each of these video IDs
3.a. Video IDs as vector
```{r}
rel_video_ids <- base::as.vector(q2$rel_video_id)
```
3.b. Get related videos function
```{r}
 get_all_rel_vids <- function(id) {
  tuber::get_related_videos(id, max_results = 50, safe_search = "none")
} 
```
3.c. Iterations (get 50 related videos for each video)
```{r}
q3 <- purrr::map_df(.x = rel_video_ids, 
                    .f = get_all_rel_vids)
```
Check there are 50 related for each video
```{r}
q3 %>% count(video_id)
```
Unique channels
```{r}
q3_channels <- q3 %>% 
  group_by(channelId) %>% sample_n(1)
```

```{r}
```


```{r}
```




