---
title: "Week 4 Assignment"
author: "Fernan Gaillardou"
date: "2022-10-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Questions

1.  Count the types of things I'm doing online (column "transType" in the `wbdata`). What is my most frequent type of interaction with the web?
```{r}
wbdata %>%
  group_by(transType) %>% 
  count() %>% 
  ggplot() +
  geom_bar(aes(transType, n), stat = "identity") +
  coord_flip()
```
2.  Change the colour of the bars in the bar graph.
```{r}
wbdata %>%
  group_by(transType) %>% 
  count() %>% 
  ggplot() +
  geom_bar(aes(transType, n, fill=transType), stat = "identity") +
  coord_flip()
```
Order bars (still working on it)
```{r}
wbdata %>%
  group_by(transType) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  ggplot() +
  geom_bar(aes(transType, n, fill=transType), stat = "identity")
```
### Questions

1.  Count how many "left" nodes there are and how many "right" nodes there are.

```{r}
question1 <- samp_attr_lr %>%
  group_by(lr) %>% 
  count() 
```
2.  Add arrows to the network plot and increase their width (hint: see [here](https://r-graph-gallery.com/248-igraph-plotting-parameters.html))
```{r}
plot(simplify(igraph_rt_samp), 
     vertex.label = NA, 
     vertex.size = 4,
     vertex.color = samp_attr_lr$lrcolor,
     edge.arrow.size = 0.1,
     edge.arrow.width=0.1)
```